---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# my.project

<!-- badges: start -->
<!-- badges: end -->

The goal of my.project is to perform three functions. 

## Installation

You can install the development version of my.project from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jaceywebber/Webber_pkg")
```

Packages that you will need: 

```{r example}
library(my.project)
library(tidyverse)
library(ggplot2)
```

First function: cleaning_data: 
This function will remove all NA values from the data. 


```{r}
cleaning_data("Data/surveys.csv")
```


Second function: create_plot
This function will create a jitter plot from the data with the sex on the x-axis, weight on the y-axis, and categorized sex by color. 

```{r}
create_plot("Data/surveys.csv")
```
Third function: linear_model
This function will generate a linear model and summary from the data with hindfoot_length as the response and weight as the predictor. 

```{r}
linear_model("Data/surveys.csv")
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

